---
title: "Toolik Station Air Temperature"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(here)
# janitor is great for data cleaning
library(janitor)
library(skimr)
```

## Read in the Toolik Lake meteorologic data

**Data:** Shaver, G. 2019. A multi-year DAILY weather file for the Toolik Field Station at Toolik Lake, AK starting 1988 to present. ver 4. Environmental Data Initiative. https://doi.org/10.6073/pasta/ce0f300cdf87ec002909012abefd9c5c (Accessed 2021-08-08).

The data are stored in the `data-raw` subfolder. We'll use `here::here()` to point to it, and read it in using the `readr::read_csv()` function from the `readr` package (part of the `tidyverse`). 

```{r}
# here() in the console will tell me what directory you are in
# look in data to data-raw, and look for toolik_weather.csv
toolik_weather <- read_csv(here::here("data", "data-raw", "toolik_weather.csv"))
# fix naming convention using pipe operator = %>% (tidyverse) or |> (base r package)
toolik_weather_2 <- read_csv(here::here("data", "data-raw", "toolik_weather.csv")) %>%
  # defaults to lower snake case
  janitor::clean_names()

#fix NA values
toolik_weather_3 <- read_csv(here::here("data", "data-raw", "toolik_weather.csv"),
  na = "#N/A") %>%
# defaults to lower snake case
  janitor::clean_names()
```


```{r}
names(toolik_weather_3)
```

## Make a graph

Let's make a jitterplot of temperatures by month. 
```{r}
toolik_mean_temp_jitter <- ggplot(data = toolik_weather_3, aes(x = as.factor(month), y = daily_air_temp_mean_c)) +
  geom_jitter(aes(color = daily_air_temp_mean_c), show.legend = FALSE) +
  scale_color_gradient(low = "blue", high = "orange") +
  theme_minimal() +
    labs(title = "Toolik Station daily air temperature",
       x = "Month",
       y = "Daily mean air temperatures (Celsius)")

toolik_mean_temp_jitter
```


## Export a figure

```{r}
# creating a saved chart
ggsave(here::here("figs", "toolik_mean_temp_jitter.png"), height = 5, width = 6)
```


## End Example 1
